Main Analyses

### 2016-03-01 Rmd/main-analysis.Rmd
Submitted version 29/2/2016

### All 4 together
```{r, eval = FALSE}
ybl <- list(yb1 <- c(1, 1))
step <- 0.05
cnames <- c("C", "BD", "COST")
ps <- round(do.call(rbind, pareto_steps(cnames, step)), 2); head(ps)
Yv = "conv_area"; Cv = "tot_C"; #BDv = "int_prior"; COSTv = "mu_cost"
BDv = c(Yv, "int_prior"); COSTv = c(Yv, "mu_cost")
wmu <- function(x, na.rm = na.rm) {
  weighted.mean(x = x[, 2], w = x[, 1], na.rm = na.rm)
}
Yst = sum; Cst = sum; BDst = wmu; COSTst = wmu
crops <- list(c("maize", "soy"))
croplnms <- list("both")

@@

# plot(ybdc$maize$heat)
# par(mfrow = c(1, 2))
# plot(ycost$maize$heat)
# plot(ycost$soy$heat)
# plot(ycost$both$heat)
# plot(bdc$both$heat)
# save(ybdc, cbdc, ycost, bdc, file = fp(p_out, "mainresults1502.rda"))
# save(ybdc, ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
save(ybdc, file = fp(p_out, "mainresults2502.rda"))
# load(fp(p_out, "mainresults1702.rda"))
```
<a href="#top">Back to top</a>

>>>>

### All 4 together
```{r, eval = FALSE}
ybl <- list(yb1 <- c(1, 1))
step <- 0.05
cnames <- c("C", "BD", "COST")
ps <- round(do.call(rbind, pareto_steps(cnames, step)), 2); head(ps)
Yv = "conv_area"; Cv = "tot_C"; #BDv = "int_prior"; COSTv = "mu_cost"
# BDv = c(Yv, "int_prior"); COSTv = c(Yv, "mu_cost")
# wmu <- function(x, na.rm = na.rm) {
#   weighted.mean(x = x[, 2], w = x[, 1], na.rm = na.rm)
# }
Yst = sum; Cst = sum; # BDst = wmu; COSTst = wmu
crops <- list(c("maize", "soy"))
croplnms <- list("both")

@@

# plot(ybdc$maize$heat)
# par(mfrow = c(1, 2))
# plot(ycost$maize$heat)
# plot(ycost$soy$heat)
# plot(ycost$both$heat)
# plot(bdc$both$heat)
# save(ybdc, cbdc, ycost, bdc, file = fp(p_out, "mainresults1502.rda"))
# save(ybdc, ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
save(ybdc, file = fp(p_out, "mainresults2502.rda"))
# load(fp(p_out, "mainresults1702.rda"))

# 28/2 Rebuilding impacts with new travel time and bd cost metrics (totals)
load(fp(p_out, "mainresults2502.rda"))
crops <- list(c("maize", "soy"))
fnames <- imp_sorter(fp(p_out, ybdc$both$bcode), inds = 1:nrow(ybdc$both$params),                      fullnames = TRUE)
il <- input_handler("agroEcoTradeoff/external/data/ZA", crops = crops[[1]])
registerDoMC(7)
imptab <- foreach(i = 1:length(fnames)) %dopar% {  # x <- fnames[1]
  conv <- fread(fnames[i])
  impact(conv, il)
}
outtab <- do.call(rbind, lapply(1:length(imptab), function(x) {
  cbind.data.frame("iter" = x, imptab[[x]])
}))
head(outtab)

Yv = "conv_area"; Cv = "tot_C"; BDv = "cons_tot"; COSTv = "tot_cost"
Yst = sum; Cst = sum; BDst = sum; COSTst = sum
impacts <- batch_stat(outtab, Yv, Cv, BDv, COSTv, Yst, Cst, BDst, COSTst)
optitab <- non_dominator(impacts, cnames, ybdc$both$bcode)
optimal <- optitab
bpath <- "agroEcoTradeoff/external/output"
save(optimal, file = fp(bpath, paste0(ybdc$both$bcode, "/optitab2.rda")))
save(outtab, file = fp(bpath, paste0(ybdc$both$bcode, "/impacts_tab2.rda")))
# impacts[, lapply(.SD, range)]
# impacts[1765:1771, ]
# round(ybdc$both$params[1765:1771, 7:10], 2)

ybdc$both$optitab <- optimal
save(ybdc, outtab, impacts, file = fp(bpath, "mainresults2802.rda"))

```
<a href="#top">Back to top</a>
